\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2018-04-10 write_up/mixfishsim_ecolmod.tex
manuscript updates: table for models

\usepackage{lineno,hyperref}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,chains,calc}
\usepackage{hhline}
\usepackage{booktabs}
\usepackage[textsize=scriptsize]{todonotes}
%\usepackage[textsize=scriptsize, disable]{todonotes}  %% to turn off notes

@@

\begin{equation}
	Pr(J | I) = \frac{e^{-\lambda * d_{IJ}} \cdot
		(Hab_{J,p}^2 \cdot Tol_{J,p,wk})}{\sum\limits_{c=1}^{C}e^{-\lambda * d} \cdot
		(Hab_{J,p}^2 \cdot Tol_{J,p,wk})}
\end{equation}

@@

\begin{equation}
	Tol_{c, p} = \frac{1}{ \sqrt (2\pi \cdot \sigma^2_{p})} \cdot \exp(-
		\frac{(T_{c} -
		\mu_{p})^2}{2 \cdot \sigma^2_{p}} )	
\end{equation}

Where $Tol_{c,p}$ is the tolerance of population $p$ in cell $c$, $T_{c}$ is
the temperature in the cell and $\mu\added[id=PD]{_{p}}$ and
$\sigma^2\added[id=PD]{_{p}}$ the mean and standard deviation of the population
temperature tolerance. \\

@@

\begin{table}[!ht]
	\centering
	\caption{Description of variables for sub-modules}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		\multicolumn{3}{c}{\textbf{Population dynamics}}  \\
		\hhline{===}
		\multicolumn{3}{l}{\textit{Delay-difference model}} \\
		\hline
		$B_{c,d}$ & Biomass in cell $c$ and day $d$ & kg \\
		$Z_{c,d}$ & Total mortality in cell $c$ for day $d$ & - \\
		$R_{c, \tilde{y}}$  &Annualy recruited fish in cell &  yr\textsuperscript{-1} \\
		$\rho$ & Brody's growth coefficient & yr\textsuperscript{-1} \\
		$Wt_{R}$ & Weight of a fully recruited fish & kg \\
		$Wt_{R-1}$ & Weight of a pre-recruit fish & kg \\
		$\alpha_{d}$ & Proportion of annually recruited fish recruited
		during day $d$ & - \\
		\hline
		\multicolumn{3}{l}{\textit{Baranov catch equation}} \\
		\hline
		$C_{c,d}$ & Catch from cell $c$ for day $d$ & kg \\
		$F_{c,d}$ & Instantaneous rate of fishing mortality in cell $c$
		on day $d$ & - \\
		$M_{c,d}$ & Instantaneous rate of natural mortality in cell $c$
		on day $d$ & - \\
		$B_{c,d}$ & Biomass in cell $c$ on day $d$ & kg \\
		\hline
		\multicolumn{3}{c}{\textbf{Recruitment dynamics}} \\
		\hhline{===}
		$\tilde{R}_{c,d}$ & is the recruitment in cell $c$ for day $d$ & $d^{-1}$ \\
		$B_{c,d}$ & is the Biomass in cell $c$ for day $d$ & $d^{-1}$ \\
		$\alpha$ & the maximum recruitment rate & kg  \\
		$\beta$ & the biomass required to produce half the maximum rate
		of recruitment & kg \\
		\hline
		\multicolumn{3}{c}{\textbf{Population movement dynamics}} \\
		\hhline{===}
		a & b & c \\
		a & b & c \\
		\hline
		\multicolumn{3}{c}{\textbf{Fleet dynamics}} \\
		\hhline{===}
		a & b & c \\
		a & b & c \\
		\bottomrule
	\end{tabular}
\end{table}

>>>>

\usepackage{lineno,hyperref}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,chains,calc}
\usepackage{hhline}
\usepackage{booktabs}
\usepackage[textsize=scriptsize]{todonotes}
%\usepackage[textsize=scriptsize, disable]{todonotes}  %% to turn off notes
\usepackage{eurosym}

@@

\begin{equation}
	Pr(J | I) = \frac{e^{-\lambda * d_{IJ}} \cdot
		(Hab_{J,p}^2 \cdot Tol_{J,p,wk})}{\sum\limits_{c=1}^{C}e^{-\lambda * d} \cdot
		(Hab_{c,p}^2 \cdot Tol_{c,p,wk})}
\end{equation}

@@

\begin{equation}
	Tol_{c, p\added[id=PD]{, wk}} = \frac{1}{ \sqrt (2\pi \cdot \sigma^2_{p})} \cdot \exp(-
		\frac{(T_{c\added[id=PD]{, wk}} - \mu_{p})^2}{2 \cdot \sigma^2_{p}} )	
\end{equation}

Where $Tol_{c, p, \added[id=PD]{wk}}$ is the tolerance of population $p$ in
cell $c$ \added[id=PD]{in week $wk$}, $T_{c, \added[id=PD]{wk}}$ is the
temperature in the cell \added[id=PD]{given the week} and
$\mu\added[id=PD]{_{p}}$ and $\sigma^2\added[id=PD]{_{p}}$ the mean and
standard deviation of the population temperature tolerance. \\

@@

\begin{table}[!ht]
	\centering
	\caption{Description of variables for population dynamics sub-module}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		\multicolumn{3}{c}{\textbf{Population dynamics}}  \\
		\hhline{===}
		\multicolumn{3}{l}{\textit{Delay-difference model}} \\
		\hline
		$B_{c,d}$ & Biomass in cell $c$ and day $d$ & kg \\
		$Z_{c,d}$ & Total mortality in cell $c$ for day $d$ & - \\
		$R_{c, \tilde{y}}$  &Annualy recruited fish in cell &  yr\textsuperscript{-1} \\
		$\rho$ & Brody's growth coefficient & yr\textsuperscript{-1} \\
		$Wt_{R}$ & Weight of a fully recruited fish & kg \\
		$Wt_{R-1}$ & Weight of a pre-recruit fish & kg \\
		$\alpha_{d}$ & Proportion of annually recruited fish recruited
		during day $d$ & - \\
		\hline
		\multicolumn{3}{l}{\textit{Baranov catch equation}} \\
		\hline
		$C_{c,d}$ & Catch from cell $c$ for day $d$ & kg \\
		$F_{c,d}$ & Instantaneous rate of fishing mortality in cell $c$
		on day $d$ & - \\
		$M_{c,d}$ & Instantaneous rate of natural mortality in cell $c$
		on day $d$ & - \\
		$B_{c,d}$ & Biomass in cell $c$ on day $d$ & kg \\
		\hline
		\multicolumn{3}{c}{\textbf{Recruitment dynamics}} \\
		\hhline{===}
		$\tilde{R}_{c,d}$ & is the recruitment in cell $c$ for day $d$ & $d^{-1}$ \\
		$B_{c,d}$ & is the Biomass in cell $c$ for day $d$ & $d^{-1}$ \\
		$\alpha$ & the maximum recruitment rate & kg  \\
		$\beta$ & the biomass required to produce half the maximum rate
		of recruitment & kg \\
		\bottomrule
		\end{tabular}
	\end{table}

\begin{table}[!ht]
	\centering
	\caption{Description of variables for population movement sub-module}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		\multicolumn{3}{c}{\textbf{Population movement dynamics}} \\
		\hhline{===}
		\multicolumn{3}{l}{\textit{Habitat model}} \\
		\hline
		a & b & c \\
		\hline
		\multicolumn{3}{l}{\textit{Thermal tolerance}} \\
		\hline
		$T_{c,wk}$ & Temperature for cell in week & $^\circ$C \\
		$\mu_{p}$ & Mean of the thermal tolerance for population & $^\circ$C \\
		$\sigma^{2}_{p}$ & Standard deviation of thermal tolerance for
		the population & $^\circ$C \\
		\hline
		\multicolumn{3}{l}{\textit{Population movement model}} \\
		\hline
		$\lambda$ & decay rate for population movement & - \\
		$Hab^{2}_{c,p}$ & Square of habitat suitability for cell $c$ and
		population $p$ & - \\
		$Tol_{c,p,wk}$ & Thermal tolerance for population $p$ in cell
		$c$ at week $wk$ & - \\
		$d_{IJ}$ & euclidean distance between cell $I$ and cell $J$ & - \\
		\bottomrule
		\end{tabular}
	\end{table}

\begin{table}[!ht]
	\centering
	\caption{Description of variables for fleet dynamics sub-module}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		\multicolumn{3}{c}{\textbf{Short-term fleet dynamics}} \\
		\hhline{===}
		$Rev$ & Revenue from fishing tow & \euro \\
		$L_{p}$ & Landings of population $p$ & kg \\
		$Pr_{p}$ & Average price of population $p$ & \euro
		\hspace{0.1cm} kg$^{-1}$ \\
		StepL & Step length for vessel & euclidean distance \\
		Br & Bearing & degrees \\
		$k$ & Concentration parameter for Von mises distribution & - \\
		$\beta_{1}$ & shape parameter for step function & - \\
		$\beta_{2}$ & shape parameter for step function & - \\
		$\beta_{3}$ & shape parameter for step function & - \\
		\bottomrule
	\end{tabular}
\end{table}
